
\section{Introduction} %for journal use above \firstsection{..} instead


% integrate and expand
\comment{

To be effective, such tools should have several characteristics.
}


Health sensing, machine learning, network access, and computation are rapidly becoming ubiquitous, enabling new tools for capturing human activities in the natural environment.
Previous work shows such tools can be used to detect behaviors and psychological states such as stress\cite{chang2011,lu2012}, physical activity\cite{li2010,emken2012}, social interaction\cite{wyatt2011}, and smoking\cite{sazonov2011}. Likewise, there are many commercial, inexpensive, consumer-grade products (Jawbone Up, Fitbit, Nike Plus to name a few) that are putting these data in the hands of the layperson. The challenge that both laypeople and health research communities face is in making sense of this data.

Health researchers - and by extension overall public health - could benefit significantly from access to tools that leverage these data.    Many of today's greatest health challenges can be mapped back to  behavioral choices made in-the-moment.  Avoiding physical activity, eating high-fat foods, and smoking cigarettes are all poor behavioral choices made in-the-moment that, in aggreggate, lead to a variety of health problems (e.g., obesity, diabetes, heart disease, cancer, chronic pain, depression), lower quality of life and shortened lifespans \cite{franco2005, dunn2001, yanbaeva2007, ross2000}.
Similar challenges exist outside the realm of personal health.
Academic success is a function of attending class and completing assigned tasks, among other daily behaviors\cite{cooper2006}.
In personal finance, poor day-to-day purchasing decisions can add up to large financial debts\cite{norvilitis2003}.

There is a call in for the human-computer interaction (HCI), behavioral science, and other related communities to develop user interfaces for mobile behavioral interventions that help users make better in the moment behavioral choices related to health\cite{klasnja2012,nahum2012}, productivity\cite{ho2005,sohn2005,jewell2011}, and more.

With the right tools, health researchers could better examine important behavioral events and coexisting contextual factors at a level of detail and richness not previously possible.
Likewise, they can go beyond observing events.
Behavioral researchers could deliver interventions to individuals in-the-moment, and then see how the intervention in turn changes behavior and affect.

In addition to metrics of success of an intervention, behavioral theorists need tools to help understand the dynamics of behavioral responses to a stimulus.
It is due to the lack of a dynamical treatment of behavior within theories that existing models behavior appear inadequate to inform state-of-the-art intervention development \cite{riley2011}.
Applicable methods of intervention analysis and data visualization have been slow to reach behavioral researchers, dramatically limiting their ability to develop of state-of-the-art behavioral theories to address these shortcomings.
Unfortunately, the tools health researchers need to manage, review, and learn from such data do not yet exist.
New methods for evaluating these behavioral interventions remain underexplored and conventional methods of analysis do not offer the level of detail needed to explore the implicit dynamics of just-in-time, interactive, or adaptive interventions.

%Of particular interest to the health research research community is the concept of the just-in-tim

In this paper methods for analysis of the dynamical response to an intervention are outlined. The impulse reponse of a physical activity intervention is explored and data visualizations which provide insigt into the dynamics of health-related events are demonstrated.

\comment{
    % This paragraph discusses our workflow.  What did we do - step by step - to produce our contributions and reach our conclusions?
    In this paper, we derive visualizations that help behavioral scientists gain insight into the short time scale dynamics of health-related events. We focus specifically on the needs of behavioral scientists because many have access to such event datasets but do not yet have the tools to better understand health events, derive and test behavioral theories from them, and ultimately develop more effective and usable behavioral health interventions. The work can be divided into three stages.

    \textit{First}, we conduct a user needs analysis with a vested group of stakeholders. We held a data-gathering session at a top-tier behavioral science conference as well as interacted informally with behavioral scientists with specific experience and goals of capturing, analyzing and learning from pervasive health data. We also collected  and analyzed event datasets with short-time scales generated by behavioral scientists. From these interactions and data, we define a set of user goals and tasks as well as broader design considerations for behavioral health event dynamics.

    \textit{Second}, based on lessons learned from the user needs analysis, we design visualizations and demonstrate them on three datasets, each of which shows the effect of a physical activity intervention on a user. Two of the datasets were captured from children (ages 11 - ???) as they went about normal daily life, over a multi-day period (3 - 8 days).  The third dataset is a control dataset that mimics the ideal response to a "perfect" physical activity intervention.

    \textit{Third}, we derive lessons learned from the proposed visualizations, focusing on 1) what the visualizations do and do not reveal about the data, 2) where there is uncertainty in the meaning of the visualizations, and 3) what scientific questions are not answered by these visualizations and thus require future work.

    % This paragraph summarizes contributions and conclusions from the above work. % Bulleted list of 2-3 contributions
    These efforts led to the following important contributions to both the fields of behavioral science and information visualization.

    \begin{enumerate}
    	\item{a set of design considerations to guide visualization and tool design in this domain}
    	\item{introduction to intervention response dynamics in relation to developing theories}
    	\item{visualization methods which address some key tasks addressing the goals identified in the design considerations section}
    \end{enumerate}

}
% Ultimately, we conclude that ... % could just save this for the end...don't want to give away everything do we?

\comment{

%much of this will be re-integrated

Despite significant advances in the theory and practice of behavioral science, humans continue make poor behavioral choices on a daily basis, and the reasons for those choices remain, to some extent, uncharted.
The consequences of these daily choices are often insignificant in the moment but over time build up to larger individual and societal problems.






\subsubsection{Contributions}
% summarize previous work (1 paragraph)


% summarize work done (1 paragraph - maybe a long one)
}

% an alternative framing of of our contributions:
\comment{
	- to understand how we can use this type of data to accomplish these domain-specific tasks?
	- to propose new hypotheses and techniques to support these tasks?
	- to propose lessons learned that may apply for similar viz problems.


% highlight why should viz community care!
This work breaks new ground in the application domain, but also provides guidelines for future work bridging the data visualization and behavioral science communities.
}
